Enhancement of SDR in Thessaloniki

### 2024-05-14 GHI_enh_03_process.tex
Commit 2024-05-14 11:35

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-13}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-327.56 -157.11  -65.36  116.74  760.36

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)    
(Intercept)      2.431e+02  4.880e+01   4.981  9.8e-07 ***
as.numeric(Date) 6.397e-08  3.907e-08   1.637    0.102    
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 210.1 on 363 degrees of freedom
Multiple R-squared:  0.007332,  Adjusted R-squared:  0.004597 
F-statistic: 2.681 on 1 and 363 DF,  p-value: 0.1024
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-327.56 -157.11  -65.36  116.74  760.36

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)       2.431e+02  4.880e+01   4.981  9.8e-07 ***
ST_E_monthly$Date 6.397e-08  3.907e-08   1.637    0.102    
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 210.1 on 363 degrees of freedom
Multiple R-squared:  0.007332,  Adjusted R-squared:  0.004597 
F-statistic: 2.681 on 1 and 363 DF,  p-value: 0.1024
\end{verbatim}

@@

\begin{verbatim}
aa
aatm
aday
AEin1
All_daily_ratio_lim
alpha
amean
ampl
asza
atype
avar
b
BIO_ELEVA
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
fit
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
lm_mean
lm_zeropoint
mean_BR_mean
mean_BR_median
mean_BR_min
mean_mean
mean_median
mean_min
mid
MIN_ELEVA
MIN_N
mm
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
slope_mean
slope_median
slope_min
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
t
tsy
units
variables_fl
xlim
yearstodo
ylim
zeropoint
zeropointA
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-05-13 09:11:34.5 athan@sagan GHI_enh_03_process.R 3.715344 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-14}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-349.46 -163.23  -64.56  115.86  799.73

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)    
(Intercept)      1.608e+02  5.029e+01   3.198 0.001507 ** 
as.numeric(Date) 1.376e-07  4.026e-08   3.417 0.000704 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 216.5 on 363 degrees of freedom
Multiple R-squared:  0.03117,   Adjusted R-squared:  0.0285 
F-statistic: 11.68 on 1 and 363 DF,  p-value: 0.0007045
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-349.46 -163.23  -64.56  115.86  799.73

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)       1.608e+02  5.029e+01   3.198 0.001507 ** 
ST_E_monthly$Date 1.376e-07  4.026e-08   3.417 0.000704 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 216.5 on 363 degrees of freedom
Multiple R-squared:  0.03117,   Adjusted R-squared:  0.0285 
F-statistic: 11.68 on 1 and 363 DF,  p-value: 0.0007045
\end{verbatim}

@@

\begin{verbatim}
aa
aatm
aday
AEin1
All_daily_ratio_lim
alpha
amean
ampl
asza
atype
avar
b
BIO_ELEVA
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
fit
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
lm_mean
lm_zeropoint
mean_55
mean_BR_55
mean_BR_mean
mean_BR_median
mean_BR_min
mean_mean
mean_median
mean_min
mid
MIN_ELEVA
MIN_N
mm
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
slope_55
slope_mean
slope_median
slope_min
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
t
tsy
units
variables_fl
xlim
yearstodo
ylim
zeropoint
zeropointA
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-05-14 07:42:43.5 athan@tyler GHI_enh_03_process.R 11.010634 mins
\end{verbatim}

### 2024-05-14 GHI_enh_04_investigate.tex
Commit 2024-05-13 12:21
Commit 2024-05-14 11:35

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-21}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}

Attaching package: 'zoo'
\end{verbatim}

@@

\begin{verbatim}

Attaching package: 'ggpp'
\end{verbatim}

@@

lmD: 1.534136 +/- 0.10269

lmY: 1.534151 +/- 0.102692

Arima: 1.534524 +/- 0.137014

@@

lmD: 0.957882 +/- 0.154677

lmY: 0.957905 +/- 0.15468

Arima: 1.026834 +/- 0.234823

@@

lmD: 1.097965 +/- 0.167082

lmY: 1.097991 +/- 0.167085

Arima: 1.168104 +/- 0.247425

@@

lmD: 1.054627 +/- 0.240574

lmY: 1.054636 +/- 0.240578

Arima: 1.054681 +/- 0.36529

@@

lmD: 0.96011 +/- 0.254278

lmY: 0.96012 +/- 0.254282

Arima: 0.960167 +/- 0.389374

@@

lmD: 1.084083 +/- 0.073658

lmY: 1.084096 +/- 0.073659

Arima: 1.0841 +/- 0.108761

@@

lmD: 1.123441 +/- 0.069672

lmY: 1.123454 +/- 0.069673

Arima: 1.123462 +/- 0.099367

@@

lmD: 33.98221 +/- 5.725078

lmY: 33.98275 +/- 5.725178

Arima: 34.039551 +/- 9.00373

@@

lmD: 0.003272 +/- 0.000268

lmY: 0.003272 +/- 0.000268

Arima: 0.003296 +/- 0.000354

@@

lmD: 0.001727 +/- 0.000275

lmY: 0.001727 +/- 0.000275

Arima: 0.001888 +/- 0.000454

@@

lmD: 0.001702 +/- 0.000309

lmY: 0.001702 +/- 0.000309

Arima: 0.001865 +/- 0.000498

@@

lmD: 0.001878 +/- 0.000305

lmY: 0.001878 +/- 0.000305

Arima: 0.001878 +/- 0.000475

@@

lmD: 0.001807 +/- 0.000297

lmY: 0.001807 +/- 0.000297

Arima: 0.001807 +/- 0.000456

@@

lmD: 0.002392 +/- 0.000231

lmY: 0.002392 +/- 0.000231

Arima: 0.002392 +/- 0.000359

@@

lmD: 0.0026 +/- 0.000226

lmY: 0.0026 +/- 0.000226

Arima: 0.0026 +/- 0.000336

@@

lmD: 0.982152 +/- 0.142979

lmY: 0.982174 +/- 0.142982

Arima: 1.043911 +/- 0.216442

@@

lmD: 0.76413 +/- 0.10147

lmY: 0.764141 +/- 0.101472

Arima: 0.764136 +/- 0.117502

@@

lmD: 0.202029 +/- 0.037949

lmY: 0.202033 +/- 0.03795

Arima: 0.202033 +/- 0.041317

@@

lmD: 0.164435 +/- 0.03794

lmY: 0.164439 +/- 0.037941

Arima: 0.164439 +/- 0.040154

@@

lmD: 0.430568 +/- 0.042844

lmY: 0.430573 +/- 0.042845

Arima: 0.430575 +/- 0.050183

@@

lmD: -0.009715 +/- 0.019808

lmY: -0.009713 +/- 0.019809

Arima: -0.009713 +/- 0.019969

@@

lmD: -0.024545 +/- 0.018498

lmY: -0.024544 +/- 0.018499

Arima: -0.024544 +/- 0.018581

@@

lmD: 0.467007 +/- 0.072175

lmY: 0.467013 +/- 0.072176

Arima: 0.467011 +/- 0.080184

@@

lmD: 0.567078 +/- 0.082222

lmY: 0.567087 +/- 0.082223

Arima: 0.567084 +/- 0.093419

@@

lmD: 1.246547 +/- 0.136785

lmY: 1.246567 +/- 0.136788

Arima: 1.246568 +/- 0.164233

@@

lmD: 0.001291 +/- 0.000137

lmY: 0.001291 +/- 0.000137

Arima: 0.001291 +/- 0.000158

@@

lmD: 0.000409 +/- 6.1e-05

lmY: 0.000409 +/- 6.1e-05

Arima: 0.000409 +/- 7e-05

@@

lmD: 0.00033 +/- 6.4e-05

lmY: 0.00033 +/- 6.4e-05

Arima: 0.00033 +/- 7.2e-05

@@

lmD: 1.8e-05 +/- 3.3e-05

lmY: 1.8e-05 +/- 3.3e-05

Arima: 1.8e-05 +/- 3.8e-05

@@

lmD: -8e-06 +/- 3e-05

lmY: -8e-06 +/- 3e-05

Arima: -8e-06 +/- 3.5e-05

@@

lmD: 0.00091 +/- 0.000108

lmY: 0.00091 +/- 0.000108

Arima: 0.00091 +/- 0.000124

@@

lmD: 0.001059 +/- 0.000118

lmY: 0.001059 +/- 0.000118

Arima: 0.001059 +/- 0.000137

@@

lmD: 0.031908 +/- 0.003379

lmY: 0.031908 +/- 0.003379

Arima: 0.031908 +/- 0.003889

@@

lmD: 0.210914 +/- 0.239629

lmY: 0.21095 +/- 0.239633

Arima: 0.199623 +/- 0.33989

@@

lmD: 0.075139 +/- 0.179414

lmY: 0.075162 +/- 0.179417

Arima: 0.041751 +/- 0.315453

@@

lmD: 0.116601 +/- 0.178114

lmY: 0.116622 +/- 0.178117

Arima: 0.082858 +/- 0.303922

@@

lmD: -0.039715 +/- 0.164546

lmY: -0.039705 +/- 0.164548

Arima: -0.084179 +/- 0.309433

@@

lmD: -0.059533 +/- 0.164108

lmY: -0.059523 +/- 0.164111

Arima: -0.103637 +/- 0.308351

@@

lmD: 0.190061 +/- 0.219003

lmY: 0.190097 +/- 0.219007

Arima: 0.174594 +/- 0.326917

@@

lmD: 0.200402 +/- 0.22785

lmY: 0.200437 +/- 0.227854

Arima: 0.187023 +/- 0.332301

@@

lmD: 0.360189 +/- 0.242668

lmY: 0.360214 +/- 0.242672

Arima: 0.36031 +/- 0.247054

@@

lmD: 0.000562 +/- 0.000289

lmY: 0.000562 +/- 0.000289

Arima: 0.000562 +/- 0.000319

@@

lmD: 0.000393 +/- 0.000224

lmY: 0.000393 +/- 0.000224

Arima: 0.00039 +/- 0.000267

@@

lmD: 0.000413 +/- 0.000232

lmY: 0.000413 +/- 0.000232

Arima: 0.000409 +/- 0.000272

@@

lmD: 0.000208 +/- 0.000207

lmY: 0.000208 +/- 0.000207

Arima: 0.000201 +/- 0.000259

@@

lmD: 0.000192 +/- 0.000206

lmY: 0.000192 +/- 0.000206

Arima: 0.000185 +/- 0.000259

@@

lmD: 0.00056 +/- 0.000269

lmY: 0.00056 +/- 0.000269

Arima: 0.00056 +/- 0.000301

@@

lmD: 0.000566 +/- 0.000278

lmY: 0.000566 +/- 0.000278

Arima: 0.000566 +/- 0.000309

@@

lmD: 0.008619 +/- 0.005275

lmY: 0.00862 +/- 0.005275

Arima: 0.008644 +/- 0.005494

@@

Arima: 0.202033 +/- 0.041317

@@

\begin{verbatim}
Warning: Removed 26 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 13 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

lmY: 293.3335 +/- 31.54861

@@

lmY: 110.0865 +/- 10.13369

@@

lmY: 0.220182 +/- 0.057217

@@

lmY: 0.168073 +/- 0.041495

@@

\begin{verbatim}
2024-04-21 18:52:46.0 athan@tyler GHI_enh_04_investigate.R 1.292554 mins
\end{verbatim}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-14}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Attaching package: 'zoo'
\end{verbatim}

@@

\begin{verbatim}
Attaching package: 'ggpp'
\end{verbatim}

@@

lmD: 0.80888 +/- 0.10628

lmY: 0.808883 +/- 0.106282

Arima: 0.809228 +/- 0.142401

@@

lmD: 0.002077 +/- 0.154863

lmY: 0.002083 +/- 0.154866

Arima: 0.069972 +/- 0.235505

@@

lmD: 0.0726 +/- 0.167744

lmY: 0.072609 +/- 0.167747

Arima: 0.141941 +/- 0.249338

@@

lmD: -0.087078 +/- 0.239888

lmY: -0.087089 +/- 0.239892

Arima: -0.087046 +/- 0.364497

@@

lmD: -0.191061 +/- 0.253235

lmY: -0.191072 +/- 0.253239

Arima: -0.191026 +/- 0.387751

@@

lmD: 0.442171 +/- 0.074674

lmY: 0.442172 +/- 0.074676

Arima: 0.442175 +/- 0.110249

@@

lmD: 0.506855 +/- 0.071215

lmY: 0.506856 +/- 0.071216

Arima: 0.50686 +/- 0.101481

@@

lmD: -1.191149 +/- 5.69247

lmY: -1.191222 +/- 5.692569

Arima: -1.138138 +/- 8.879593

@@

lmD: 0.00182 +/- 0.000272

lmY: 0.00182 +/- 0.000272

Arima: 0.001843 +/- 0.000361

@@

lmD: 0.000729 +/- 0.00028

lmY: 0.00073 +/- 0.00028

Arima: 0.000892 +/- 0.000462

@@

lmD: 0.000678 +/- 0.000314

lmY: 0.000678 +/- 0.000314

Arima: 0.000841 +/- 0.000507

@@

lmD: 0.001176 +/- 0.000309

lmY: 0.001176 +/- 0.000309

Arima: 0.001176 +/- 0.000483

@@

lmD: 0.001189 +/- 0.000301

lmY: 0.001189 +/- 0.000301

Arima: 0.001189 +/- 0.000463

@@

lmD: 0.001144 +/- 0.000235

lmY: 0.001144 +/- 0.000235

Arima: 0.001144 +/- 0.000366

@@

lmD: 0.0013 +/- 0.00023

lmY: 0.001301 +/- 0.00023

Arima: 0.001301 +/- 0.000342

@@

lmD: 0.376507 +/- 0.145413

lmY: 0.376518 +/- 0.145415

Arima: 0.436011 +/- 0.220423

@@

lmD: 0.319795 +/- 0.10019

lmY: 0.319795 +/- 0.100192

Arima: 0.3198 +/- 0.116665

@@

lmD: 0.10702 +/- 0.036516

lmY: 0.107021 +/- 0.036517

Arima: 0.107023 +/- 0.040195

@@

lmD: 0.108459 +/- 0.036231

lmY: 0.108461 +/- 0.036232

Arima: 0.108462 +/- 0.03848

@@

lmD: 0.144267 +/- 0.045486

lmY: 0.144265 +/- 0.045487

Arima: 0.144267 +/- 0.054102

@@

lmD: 0.022726 +/- 0.0184

lmY: 0.022726 +/- 0.0184

Arima: 0.022726 +/- 0.018993

@@

lmD: 0.018838 +/- 0.016889

lmY: 0.018838 +/- 0.016889

Arima: 0.018838 +/- 0.017339

@@

lmD: 0.194707 +/- 0.070475

lmY: 0.194706 +/- 0.070476

Arima: 0.194713 +/- 0.07858

@@

lmD: 0.227625 +/- 0.080608

lmY: 0.227625 +/- 0.080609

Arima: 0.22763 +/- 0.091764

@@

lmD: 0.447759 +/- 0.147315

lmY: 0.447759 +/- 0.147317

Arima: 0.447766 +/- 0.177904

@@

lmD: 0.000537 +/- 0.000135

lmY: 0.000537 +/- 0.000135

Arima: 0.000537 +/- 0.000157

@@

lmD: 0.000206 +/- 6e-05

lmY: 0.000206 +/- 6e-05

Arima: 0.000206 +/- 6.8e-05

@@

lmD: 0.000195 +/- 6.2e-05

lmY: 0.000195 +/- 6.2e-05

Arima: 0.000195 +/- 7e-05

@@

lmD: 4.8e-05 +/- 3.1e-05

lmY: 4.8e-05 +/- 3.1e-05

Arima: 4.8e-05 +/- 3.6e-05

@@

lmD: 3.7e-05 +/- 2.8e-05

lmY: 3.7e-05 +/- 2.8e-05

Arima: 3.7e-05 +/- 3.3e-05

@@

lmD: 0.000394 +/- 0.000106

lmY: 0.000394 +/- 0.000106

Arima: 0.000394 +/- 0.000122

@@

lmD: 0.00045 +/- 0.000117

lmY: 0.00045 +/- 0.000117

Arima: 0.00045 +/- 0.000135

@@

lmD: 0.011422 +/- 0.003629

lmY: 0.011422 +/- 0.003629

Arima: 0.011422 +/- 0.004188

@@

lmD: -1.014557 +/- 0.247144

lmY: -1.014539 +/- 0.247148

Arima: -1.025903 +/- 0.356761

@@

lmD: -1.13974 +/- 0.188386

lmY: -1.139735 +/- 0.188389

Arima: -1.172188 +/- 0.333189

@@

lmD: -1.100642 +/- 0.18719

lmY: -1.100638 +/- 0.187194

Arima: -1.133859 +/- 0.321558

@@

lmD: -1.242646 +/- 0.174098

lmY: -1.242654 +/- 0.174101

Arima: -1.284884 +/- 0.324863

@@

lmD: -1.259775 +/- 0.173629

lmY: -1.259783 +/- 0.173632

Arima: -1.301601 +/- 0.323343

@@

lmD: -1.034796 +/- 0.226955

lmY: -1.034779 +/- 0.226959

Arima: -1.050406 +/- 0.344658

@@

lmD: -1.02486 +/- 0.235592

lmY: -1.024843 +/- 0.235596

Arima: -1.038346 +/- 0.349707

@@

lmD: 0.138738 +/- 0.251457

lmY: 0.138759 +/- 0.251461

Arima: 0.138867 +/- 0.256234

@@

lmD: -0.001372 +/- 0.000292

lmY: -0.001372 +/- 0.000292

Arima: -0.001372 +/- 0.000322

@@

lmD: -0.001515 +/- 0.000226

lmY: -0.001515 +/- 0.000226

Arima: -0.001519 +/- 0.000269

@@

lmD: -0.001494 +/- 0.000234

lmY: -0.001494 +/- 0.000234

Arima: -0.001498 +/- 0.000275

@@

lmD: -0.001682 +/- 0.000209

lmY: -0.001683 +/- 0.000209

Arima: -0.00169 +/- 0.000262

@@

lmD: -0.001696 +/- 0.000208

lmY: -0.001696 +/- 0.000208

Arima: -0.001704 +/- 0.000262

@@

lmD: -0.001367 +/- 0.000272

lmY: -0.001367 +/- 0.000272

Arima: -0.001367 +/- 0.000304

@@

lmD: -0.001364 +/- 0.000281

lmY: -0.001364 +/- 0.000281

Arima: -0.001365 +/- 0.000312

@@

lmD: 0.002612 +/- 0.005505

lmY: 0.002612 +/- 0.005505

Arima: 0.002638 +/- 0.005739

@@

Arima: 0.107023 +/- 0.040196

@@

\begin{verbatim}
Warning: Removed 23 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 19 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

lmY: 129.677 +/- 37.08333

@@

lmY: 48.08231 +/- 11.89152

@@

lmY: 0.080779 +/- 0.053347

@@

lmY: 0.065639 +/- 0.040043

@@

\begin{verbatim}
2024-05-14 07:45:19.2 athan@tyler GHI_enh_04_investigate.R 2.165741 mins
\end{verbatim}
